Winter weather on exam dates and matriculation for a prestigious university in Japan

### 2023-10-25 Writeups/paper.tex
clean data cleaning codes

\title{Winter weather on exam dates and matriculation for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
%\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The author would like to thank Laura Schechter for her numerous feedback and support. I am also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions. Any errors in this draft are the sole responsibility of the author.}}
\author{
  Mizuhiro Suzuki\thanks{
    Department of Agricultural and Applied Economics, University of Wisconsin-Madison.
    Contact: msuzuki7@wisc.edu.
    The author would like to thank Laura Schechter for her numerous feedback and support.
    I am also grateful to Daiji Kawaguchi for helpful comments and suggestions.
    Any errors are the sole responsibility of the author.
  }
}
\date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}

>>>>

\title{Winter weather on exam dates and matriculation for a prestigious university in Japan}
\author{
  Mizuhiro Suzuki\thanks{
    Contact: mizuhiro.suzuki@gmail.com.
    The author would like to thank Laura Schechter for her numerous feedback and support.
    I am also grateful to Daiji Kawaguchi for helpful comments and suggestions.
    Any errors are the sole responsibility of the author.
  }
}
\date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}
